---
title: "High Temperatures"
author: "Ryan"
execute:
    echo: FALSE
    warning: FALSE
    message: FALSE
---

This R script uses the **worldmet** package to download real hourly weather data for **Seattle Tacoma International Airport** for the year **2024**. It filters the data to focus on the month of **July** and calculates the maximum daily temperature in **Celsius**, then converts these temperatures to **Fahrenheit**. Finally, it visualizes the daily high temperatures throughout July 2024 using a clear and informative line chart created with **ggplot2**. This approach allows for easy exploration of **historical temperature trends** without the need for **API tokens** or complex setups.



```{r}
library(worldmet)
library(dplyr)
library(lubridate)
library(ggplot2)
```

```{r}
stations <- getMeta()
seattle_stations <- subset(stations, grepl("SEATTLE", station, ignore.case = TRUE))


station_id <- "727930-24233"

seattle_weather <- importNOAA(
  code = station_id,
  year = 2024,
  hourly = TRUE,
  path = tempdir()
)

daily_max_temps <- seattle_weather %>%
  mutate(date = as.Date(date)) %>%
  filter(month(date) == 7) %>%
  group_by(date) %>%
  summarise(tmax_C = max(air_temp, na.rm = TRUE)) %>%
  mutate(tmax_F = round(tmax_C * 9/5 + 32, 1))

ggplot(daily_max_temps, aes(x = date, y = tmax_F)) +
  geom_line(color = "#0072B2", size = 1.2) +
  geom_point(color = "#D55E00", size = 2) +
  labs(
    title = "Seattle Daily High Temperatures (°F) — July 2024",
    x = "Date",
    y = "Max Temperature (°F)"
  ) +
  theme_minimal(base_size = 14)

```



